---
title: "Bootstrapping"
subtitle: "20201124"
output: github_document
---


```{r setup, include = FALSE}
library(tidyverse)
library(modelr)
library(mgcv)
library(p8105.datasets)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d

set.seed(1)
```


## Simulate data
```{r}
n_samp = 250

sim_df_const = 
  tibble(
    x = rnorm(n_samp, 1, 1),
    error = rnorm(n_samp, 0, 1),
    y = 2 + 3 * x + error
  )

sim_df_nonconst = sim_df_const %>% 
  mutate(
  error = error * .75 * x,
  y = 2 + 3 * x + error
)
```


Plot the datasets.

```{r}
sim_df = 
  bind_rows(const = sim_df_const, nonconst = sim_df_nonconst, .id = "data_source") 

sim_df %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_point(alpha = .5) +
  stat_smooth(method = "lm") +
  facet_grid(~data_source) 
```


```{r}
lm(y ~ x, data = sim_df_const) %>% 
  broom::tidy() %>% 
  knitr::kable(digits = 3)

lm(y ~ x, data = sim_df_nonconst) %>% 
  broom::tidy() %>% 
  knitr::kable(digits = 3)
```


## Draw on bootstrap sample

```{r}
boot_sample = function(df) {
  
  sample_frac(df, replace = TRUE) %>% 
    arrange(x)
  
}
```

why do we want to draw the same size ?
because confidence interval/ variance estimate are really dependent on sample size.
we want to mimic the uncertainty in the dataset, with replacement, but remain the sample size the same. 


check if this works...
```{r}
boot_sample(sim_df_nonconst) %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_point(alpha = .3) +
  stat_smooth(method = "lm") +
  ylim(-5 ,16)
```

```{r}
boot_sample(sim_df_nonconst) %>% 
  lm(y ~ x, data = .) %>% 
  broom::tidy()
```


## Many samples and analysis

```{r}
boot_straps = 
  data_frame(
    strap_number = 1:1000,
    strap_sample = rerun(1000, boot_sample(sim_df_nonconst))
  )

#or

boot_straps = 
  tibble(
    strap_number = 1:1000,
    strap_sample = rerun(1000, boot_sample(sim_df_nonconst))
  )

boot_straps
```


Can I run my analysis on these...?

```{r}
boot_results =
  boot_straps %>% 
  mutate(
    models = map(.x = strap_sample, ~lm(y ~ x, data = .x)),
    results = map(models, broom::tidy)
  ) %>% 
  select(strap_number, results) %>% 
  unnest(results)
  
boot_results
```

What do I have now?

```{r}
boot_results %>% 
  group_by(term) %>% 
  summarize(
    mean_est = mean(estimate),
    se_est = sd(estimate))
```

Look at the distributions

```{r}
boot_results %>% 
  filter(term == "x") %>% 
  ggplot(aes(x = estimate)) +
  geom_density()
```

construct bootstrap CI

```{r}
boot_results %>% 
  group_by(term) %>% 
  summarize(
    ci_lower = quantile(estimate, 0.025), 
    ci_upper = quantile(estimate, 0.975))
```


## Bootstrap using modelr 

Can we simplify anything ...?

```{r}
sim_df_nonconst %>% 
  bootstrap(1000, id = "strap_number") %>% 
  mutate(
    models = map(.x = strap, ~lm(y ~ x, data = .x)),
    results = map(models, broom::tidy)
  ) %>% 
  select(strap_number, results) %>% 
  unnest(results) %>% 
  group_by(term) %>% 
  summarize(
    mean_est = mean(estimate),
    se_est = sd(estimate))
  
```



## Revist the nyc airbnb

```{r}
data("nyc_airbnb")

nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(stars = review_scores_location / 2) %>% 
  rename(
    borough = neighbourhood_group,
    neighborhood = neighbourhood) %>% 
  filter(borough != "Staten Island") %>% 
  select(price, stars, borough, neighborhood, room_type)
```


```{r}
nyc_airbnb %>% 
  ggplot(aes(x = stars, y = price, color = room_type)) + 
  geom_point() 
```



```{r}
nyc_airbnb %>% 
  filter(borough == "Manhattan") %>% 
  drop_na(stars) %>% 
  bootstrap(1000, id = "strap_number") %>% 
  mutate(
    models = map(.x = strap, ~lm(price ~ stars, data = .x)),
    results = map(models, broom::tidy)
  ) %>% 
  select(strap_number, results) %>% 
  unnest(results) %>% 
  group_by(term) %>% 
  summarize(
    mean_est = mean(estimate),
    se_est = sd(estimate))
```



Compare this to 'lm':

```{r}
nyc_airbnb %>% 
  filter(borough == "Manhattan") %>% 
  drop_na(stars) %>%
  lm(price ~ stars, data = .) %>% 
  broom::tidy()
```




```{r}
airbnb_boot_results =
  nyc_airbnb %>% 
  filter(borough == "Manhattan") %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(
    models = map(strap, ~ lm(price ~ stars + room_type, data = .x)),
    results = map(models, broom::tidy)) %>% 
  select(results) %>% 
  unnest(results) %>% 
  filter(term == "stars") %>% 
  ggplot(aes(x = estimate)) + 
  geom_density()

airbnb_boot_results
```







